Baseline centering problem

### 2018-12-11 paper/tangotd.tex

>>>>

This contains: Section 1: remarks on recovering the known convergence results
for TD in a single framework, plus ideas on systematic variants. Section
2: the problem of the existence of near-solutions to the Bellman equation
that are very far from the true value function (I think this is quite
serious off-policy). Section 3: Ideas on how, even if there's no reward
signal, we should still learn how to navigate in the Markov chain and
learn which actions/policy to use to go to which states (this extends
eligibility traces in a systematic way).
